A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-09-04 paper.Rmd
update limitation

Human evaluation of residuals is expensive, time-consuming and laborious. This is possibly why residual plot analysis is often not done in practice. However, with the emergence of effective computer vision, our work could lay a foundation for automated residual plot assessment.

- The possiblity of computer vision in the future.

- repeat the scope of the study
- list other things we could have tested
- explain why the result should apply to other residual diagnostics settings 
- finding interesting feature that was not intended to test for

>>>>

Additionally, there is the exciting possibility of utilizing computer vision technology to automate the analysis of lineup of residual plots. This innovation has the potential to significantly reduce the expenses associated with recruiting human judges. By incorporating computer vision models, researchers can simplify the evaluation process, making it more efficient and cost-effective.

The scope of this study is to highlight practical value of residual plots in model diagnostics, drawing comparisons with conventional tests. Our primary focus is on the use of residual-fitted plots in a controlled model environment for the purpose of a human subject experiment. It's important to note that there are other intriguing aspects of residual diagnostics that fall beyond the boundaries of this paper. For example, as mentioned in Introduction, residual plots can be used to explore interesting data characteristics while conducting model diagnostics. Furthermore, some model violations, such as serial correlation, necessitate the use of alternative residual plots like residual against row number plots. Nevertheless, we believe that the insights derived from this study have the potential to apply to other residual diagnostics setting, because the fundamental principles and statistical concepts underlying the lineup protocol and residual plots remain consistent across different contexts. In real-world situations, researchers often rely on visual assessment to make informed decisions about model validity. The lineup protocol's capability to identify deviations from randomness serves as a valuable aid in this scenario.

### 2023-09-04 paper.tex
update limitation

\begin{itemize}
\item
  explain how the lineup protocol can be cheaply done with the R package
  ``nullabor''. everyone can do it easily. The cost of using lineup in
  stat education under classroom setting is cheap (adam loy teaching
  paper)
\item
  Formal tests. reliable results. crowd sourcing is not expensive
  compared to the cost other devices in the lab and is not entirely
  unreasonable. Only if there is grey area (you can not confidently
  detect the data).
\item
  The possiblity of computer vision in the future.
\item
  repeat the scope of the study
\item
  list other things we could have tested
\item
  explain why the result should apply to other residual diagnostics
  settings
\item
  finding interesting feature that was not intended to test for
\end{itemize}

>>>>

One of the notable limitations of the lineup protocol lies in its
reliance on human judgements. In this context, the effectiveness of the
lineup protocol is closely connected with the perceptive ability and
subjective interpretation of individual evaluators. This reliance on
human judgment introduces an element of variability and subjectivity
that can potentially impact the robustness of the results obtained. To
ensure reliable outcomes, it's often necessary to include a diverse
group of participants capable of offering unbiased judgements. This
requirement has led researchers, including those in our study, to turn
to crowd-sourcing platforms that offer access to a random selection of
participants, which can help mitigate potential bias.

It is worth noting that despite the need for participants with unbiased
perspectives, the lineup protocol can be implemented at a relatively low
cost. Leveraging tools like the R package \texttt{nullabor}, the process
of constructing and evaluating lineups becomes accessible and
straightforward. This accessibility empowers a wider range of
researchers, even those without extensive statistical backgrounds, to
employ the lineup protocol in their studies. Moreover, the
cost-effectiveness of lineup-based analyses makes them particularly
appealing for integration into statistical education within classroom
settings (cite adam loy paper here). The practicality of lineup
demonstrations can facilitate a deeper understanding of the concept of
randomness and statistical testing among students.

However, it's important to understand that if the goal is to attain
results similar to those of formal hypothesis testing in rigor and
reliability, using crowd-sourcing becomes necessary. The expense
associated with crowd-sourcing is relatively reasonable when compared to
the costs of other laboratory devices, making it a sensible investment
for research that requires clear and valuable findings. Importantly,
this higher level of scrutiny is typically justified only when the data
plot can not be confidently identified and requires a thorough
investigation.

Additionally, there is the exciting possibility of utilizing computer
vision technology to automate the analysis of lineup of residual plots.
This innovation has the potential to significantly reduce the expenses
associated with recruiting human judges. By incorporating computer
vision models, researchers can simplify the evaluation process, making
it more efficient and cost-effective.

The scope of this study is to highlight practical value of residual
plots in model diagnostics, drawing comparisons with conventional tests.
Our primary focus is on the use of residual-fitted plots in a controlled
model environment for the purpose of a human subject experiment. It's
important to note that there are other intriguing aspects of residual
diagnostics that fall beyond the boundaries of this paper. For example,
as mentioned in Introduction, residual plots can be used to explore
interesting data characteristics while conducting model diagnostics.
Furthermore, some model violations, such as serial correlation,
necessitate the use of alternative residual plots like residual against
row number plots. Nevertheless, we believe that the insights derived
from this study have the potential to apply to other residual
diagnostics setting, because the fundamental principles and statistical
concepts underlying the lineup protocol and residual plots remain
consistent across different contexts. In real-world situations,
researchers often rely on visual assessment to make informed decisions
about model validity. The lineup protocol's capability to identify
deviations from randomness serves as a valuable aid in this scenario.
